Data preparation for team category analysis

### 2023-05-17 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Adding day of week proportion telework.

Join working days, working days per status, and team members into one datafram by `supervisor_e_mail_address`.

@@

```{r}
prep_building <- 
  prep_building %>% 
  left_join(prep_xx)
```
# CONTINUE FROM HERE

-   Modal size of team over observation window

-   Proportion of team members exiting team

-   Proportion of working days at least two team member co-located

-   Proportion of working days supervisor is co-located with at least
    one team member

-   Proportion of working days entire team is co-located

-   Proportion of working days entire team is remote

-   Proportion of observation window the team existed.

### Employee, day of week variables

@@

We make the same calculations as above, but by the day of the week.

```{r}
prep_day_of_week <-
  cohort_panel %>%
  group_by(person_id,daily_status_imputed,date_day_of_week,) %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup() %>% 
  pivot_wider(values_from = working_days, names_from = c(daily_status_imputed)) %>% 
  left_join(observation_window_days_day_of_week) %>% 
  clean_names() %>% 
  rename_with(~glue::glue("daily_status_{.}"), c(-person_id,-date_day_of_week,-observation_window_days))  %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  ) %>% 
  mutate(
    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
  )  %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

```{r}
prep_day_of_week %>% 
  skim()
```

@@

```{r}
prep_xx <- 
  prep_day_of_week %>% 
  select(person_id,date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
  pivot_longer(cols = starts_with("daily_status")) %>% 
  mutate(date_day_of_week = str_to_lower(date_day_of_week)) %>% 
  unite("name",date_day_of_week,name) %>% 
  pivot_wider(values_from = value, names_from = name) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

>>>>

Join working days, working days per status, and team members into one dataframe by `supervisor_e_mail_address`.

@@

### Team, day of week variables

@@

First count the number of distinct days per `supervisor_e_mail_address`, `date_day_of_week`, `person_id`, and `daily_status_imputed`, then filter to daily status: *Reporting to Job Site* or *Teleworking*.

```{r}
prep_a <-
  cohort_panel %>%
  group_by(supervisor_e_mail_address,person_id,daily_status_imputed,date_day_of_week,.drop = FALSE) %>% 
  summarise(working_days = n_distinct(date)) %>% 
  ungroup() %>% 
  filter(
    daily_status_imputed == "Reporting to Job Site" |
      daily_status_imputed == "Teleworking"
  )
```

@@

Second, sum the number days by `supervisor_e_mail_address` and `date_day_of_week` from dataframe `prep_a`.

```{r}
prep_b <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address,date_day_of_week) %>% 
  summarise(
    working_days = sum(working_days)
  ) %>% 
  ungroup()
```

Third, sum the number days by `supervisor_e_mail_address`, `date_day_of_week` and `daily_status_imputed` from dataframe `prep_a` and reshape the data wide so that statuses are in columns, `daily_status_*`.

```{r}
prep_c <- 
  prep_a %>% 
  group_by(supervisor_e_mail_address,daily_status_imputed,date_day_of_week) %>% 
  summarise(
    working_days = sum(working_days)
  ) %>% 
  ungroup() %>% 
  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
  clean_names() %>% 
  rename_with(~glue::glue("daily_status_{.}"), c(-supervisor_e_mail_address,-date_day_of_week))
```

Fourth, count the number of unique team members per `supervisor_e_mail_address` and `date_day_of_week`.

```{r}
prep_d <-
  cohort_panel %>%
  group_by(supervisor_e_mail_address,date_day_of_week) %>% 
  summarise(
    team_members = n_distinct(person_id)
  ) %>% 
  ungroup()
```

Join working days, working days per status, and team members into one dataframe by `supervisor_e_mail_address`.

```{r}
prep_e <- 
  prep_b %>% 
  full_join(prep_c) %>% 
  full_join(prep_d) %>% 
  left_join(observation_window_days_day_of_week)
```

Review data by `date_day_of_week`.

```{r}
prep_e %>% 
  group_by(date_day_of_week) %>% 
  skim()
```

Filter out *Sat* and *Sun* as there are no working days.

```{r}
prep_f <- 
  prep_e %>% 
  filter(date_day_of_week != "Sat" &
           date_day_of_week != "Sun")
```

```{r}
prep_g <- 
  prep_f %>% 
  mutate(
    observation_window_days = team_members*observation_window_days,
    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
  ) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

```{r}
prep_g %>% 
  skim()
```

@@

```{r}
prep_xx <- 
  prep_g %>% 
  select(supervisor_e_mail_address,
         date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
  pivot_longer(cols = starts_with("daily_status")) %>% 
  mutate(date_day_of_week = str_to_lower(date_day_of_week)) %>% 
  unite("name",date_day_of_week,name) %>% 
  pivot_wider(values_from = value, names_from = name) %>% 
  mutate(
    across(
      .cols = where(is.numeric),
      .fns = ~replace_na(.,0)
    )
  )
```

@@

# CONTINUE FROM HERE

<!-- -   Modal size of team over observation window -->

<!-- -   Proportion of team members working days remote by the day of the -->
<!--     week -->

<!-- -   Proportion of team members exiting team -->

<!-- -   Proportion of working days at least two team member co-located -->

<!-- -   Proportion of working days supervisor is co-located with at least -->
<!--     one team member -->

<!-- -   Proportion of working days entire team is co-located -->

<!-- -   Proportion of working days entire team is remote -->

<!-- -   Proportion of observation window the team existed. -->
